### 2023-04-24 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

In conclusion, the goals of this project have been largely accomplished. The implementation of a Python routine for complete automation and integration of the system has significantly improved the precision of experiments and enabled real-time collection of extensive data without requiring the expertise and time of a specialized scientist. The success of this project underscores the potential of automation in enhancing scientific research and accelerating progress towards achieving research goals.
In addition to its potential in scientific research, the software developed in this project can also be leveraged by industrial approaches. Furthermore, the classification methods and system control implemented in this project have yielded promising results and can be further optimized in the future. Overall, this project serves as a valuable contribution towards the advancement of automated systems and the optimization of experimental processes, with broad implications for both research and industrial applications.

The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
The previous student work was more focused on detecting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
From the work I've done it highlights:

@@

        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzyfied.
        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.

        For that, I tried to fuzzyfy the controller input by the data acquired in the step routine. With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
                \caption{Fuzzyfication}
                \label{fig:fuzzy_input}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
                \caption{Defuzzyfication}
                \label{fig:fuzzy_output}
            \end{figure}

        \begin{figure}[H]
            \centering
            \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
            \caption{Fuzzy Rules}
            \label{fig:fuzzy_rules}
        \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
                \caption{Test 1: fuzzy controller}
                \label{fig:fuzzy_test1}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
                \caption{Test 2: fuzzy controller}
                \label{fig:fuzzy_test2}
            \end{figure}

>>>>

In conclusion, the implementation of a Python routine for complete automation and integration of the system has improved the precision of experiments and enabled real-time collection of extensive data without requiring the expertise and time of a specialized scientist. 
This project underscores the potential of automation in enhancing scientific research and accelerating progress towards achieving research goals.
In addition to its potential in scientific research, the software developed in this project can also be leveraged by industrial approaches. 
Furthermore, the classification methods and system control implemented in this project have yielded promising results and can be further optimized in the future. Overall, this project serves as a contribution towards the advancement of automated systems and the optimization of experimental processes.

To continue, my proposal would be to prioritize the improvement of the classification step. 
Ideally, we could use machine learning or another algorithm to ensure accurate classification of individual data samples.

By achieving a reliable classification, we can then implement more effective controller logic or approaches. 
In this regard, I would like to present the concept of a fuzzy controller as a potential solution.

To finish, I would propose a final investment in the system portability so that it can be applicable in remote applications.

\subsection{Machine Learning}

        One challenge in implementing the controller is that we do not have continuous feedback. 
        Instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
        As this project involves logical control, it requires a different approach.

        The fuzzy approach is an attempt to quantify the classification and fit different control models.

        For that, I fuzzyfied the controller input with the data acquired in an experiment of step routine\ref{subsec:step_routine}. With the data, I mapped the area of each spraying mode according to its potential as shown in the Figure \ref{fig:fuzzy_input}.
        Figures \ref{fig:Fuzzyfication} and \ref{fig:defuzzyfication} shows the steps of fuzzyfication and defuzzyfication between the input and output of the controller.

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
                \caption{Fuzzyfication of the voltage input}
                \label{fig:fuzzy_input}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
                \caption{Defuzzyfication of output}
                \label{fig:fuzzy_output}
            \end{figure}

        Our controller is a machine that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules.
        The rules are listed bellow.

        Fuzzy Rules:

        -> IF dripping THEN increase

        -> IF intermittent THEN increase

        -> IF cone jet THEN stabilize

        -> IF multi jet THEN decrease

        -> IF corona THEN decrease

        % \begin{figure}[H]
        %     \centering
        %     \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
        %     \caption{Fuzzy Rules}
        %     \label{fig:fuzzy_rules}
        % \end{figure}

        For testing the concept I've showed two possible states where the voltage is bellow the necessary to stabilize in cone jet and when is above that voltage. We can see in figures \ref{fig:fuzzy_test1} and \ref{fig:fuzzy_test2} that each test the output was either increase or decrease the actuator signal.

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
                \caption{Test 1: fuzzy controller. Input voltage 4000 V the controller output to increase the voltage.}
                \label{fig:fuzzy_test2}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
                \caption{Test 2: fuzzy controller. Input voltage 7000 V the controller output to decrease the voltage.}
                \label{fig:fuzzy_test1}
            \end{figure}

        Note that, for this method to work it is needed to run a step sequence to scan the cone jet stability island. With that data, create the input membership function. Then, run the controller routine in fuzzy mode.

    \subsection{System Portability}
    \label{subsec:portability}

        Raspberry Pi

    \section{Final Discussions}

        The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
        The previous student work was focused in predicting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
        From the development done by me, it highlights the results:

@@

### 2023-04-24 Documentation/UFMG/PFCII/Results/Results.tex
documentation

The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. Most power supplies available in the market rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person. Moreover, manual adjustment takes some time to achieve the desired voltage. By running a computer routine that automatically sends commands to the power supply, we can achieve faster and more reliable experiment data.
We can see in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp} the visual interface that the operator have during an experiment. All the important data of EHDA experiments are showed in the same screen and referring to each 0.5 seconds sampling time.

\begin{figure}[H]
    \center
    \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
    \caption{Print screen of the window shows user interface during the experiment.
        We can see the image generated by the camera in the background.
        The routine code running in pycharm software on the right side.
        And also real time signal plottings of the current data on the left side.}
        \label{fig:multi_class_exp1}
\end{figure}

\begin{figure}[H]
    \center
    {\includegraphics[width=17cm]{Figuras/19:03/axs2.png}}
    \caption{Print screen during an experiment. At this moment we are in Multi Jet spraying mode. At the left we can see the current signal has a smooth and constant curve. We can also see the automatic classification on the right side.}
    \label{fig:multi_class_exp}
\end{figure}

@@

The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes difficult the controller development.

@@

For validation purposes and also to expose the benefits of the automated routine and classification

    For better understand the effects of both voltage and flow rate in the spraying dynamics manual experiments were made.
    Also in order to find the stability region of cone jet mode for the liquid and setup used.

    \begin{figure}[H]
        \center
        \includegraphics[width=12cm]{Figuras/regions.png}
        \caption{ exp-26-01-2 (V x Q)}
    \end{figure}

    For validation of the automatic system and classification some experiments were made having both manual and automatic data collecting.

    In Figure 14 we can see a result of the map generated by the automatic classification in this experiment.

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=8cm]{Figuras/april/manual_stability.png}
            \caption{ exp-26-01 manual classification}
        \end{figure}

        \begin{figure}[H]
            \center
            \includegraphics[width=9cm]{Figuras/report3/map-exp-26-01.png}
            \caption{ exp-26-01 automatic classification}
        \end{figure}

>>>>

The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. Most power supplies available in the market rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person. Moreover, manual adjustment takes some time to achieve the desired voltage. By running a computer routine that automatically sends commands to the power supply and pump machine we can achieve faster and more reliable experiment data.
We can see in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp} the visual interface that the operator have during an experiment. All the important data of EHDA experiments are showed in the same screen and referring to each 0.5 seconds sampling time.

\begin{figure}[H]
    \center
    \includegraphics[width=16cm]{Figuras/19:03/axs1.png}
    \caption{Print screen of the window shows user interface during the experiment.
        We can see the image generated by the camera in the background.
        The routine code running in pycharm software on the right side.
        And also real time signal plottings of the current data on the left side.}
        \label{fig:multi_class_exp1}
\end{figure}

\begin{figure}[H]
    \center
    {\includegraphics[width=16cm]{Figuras/19:03/axs2.png}}
    \caption{Print screen during an experiment. At this moment we are in Multi Jet spraying mode. At the left we can see the current signal has a smooth and constant curve. We can also see the automatic classification on the right side.}
    \label{fig:multi_class_exp}
\end{figure}

@@

The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes it hard to control this process.

@@

For validation purposes and also to expose the benefits of the automated routine and classification the map sequence proof itself the best result of this work.

    Firstly, for better understand the spraying dynamics, manual experiments were done.
    Figure \ref{fig:stability_1} shows the stability region of different spraying mode for pure ethanol in the range of voltage and flow rate.

    \begin{figure}[H]
        \center
        \includegraphics[width=12cm]{Figuras/regions.png}
        \label{fig:stability_1}
        \caption{Spraying modes regions of pure ethanol}
    \end{figure}

    For validation of the automatic classification experiments were made comparing both manual and automatic classification.
    In figures \ref{fig:stability_2} and \ref{fig:stability_3} we can see that the cone jet stability island has a similar shape in both manual (fig. \ref{fig:stability_2}) and automatic (fig. \ref{fig:stability_3}). This

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=8cm]{Figuras/april/manual_stability.png}
            \caption{ exp-26-01 manual classification}
            \label{fig:stability_2}
        \end{figure}

        \begin{figure}[H]
            \center
            \includegraphics[width=9cm]{Figuras/report3/map-exp-26-01.png}
            \caption{ exp-26-01 automatic classification}
            \label{fig:stability_3}
        \end{figure}
